How to be a good member of a scientific software community [Article v\versionnumber]

### 2022-01-05 paper.tex
added request for plain text bug reports

>>>>

    \item For a command line tool, provide the command line and configuration
    information in plain text, \emph{NOT} as a screen shot. A screen shot is
    often harder to read, and at a bare minimum forces the developer to retype
    your command instead of copying and pasting, which makes it harder for them
    to spot possible typos, etc.
